---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ResampleProps

The goal of ResampleProps is to ...

## Installation

The `devtools` library for R allows package installation from GitHub

``` r
devtools::install_github("robertwwalker/ResampleProps")
```

# Examples

There are four commands of similar structure: ResampleMean, ResampleProp, ResampleDiffMeans, ResampleDiffProps.  I will show an example of a single mean.  The proportions calculations rely on binary data transformed to a table.  There is an option `tab.col` that allows one to select which column of the proportions table is of interest.  This simply owes to R's alphabetizing factors.

## A Single Mean

Resampling a single mean 1000 times is easy.

```{r ex2}
library(ResampleProps)
My.LNorm.Means <- ResampleMean(rlnorm(100))
summary(My.LNorm.Means)
```
### Plot of the Resampled Means

```{r}
plot(density(My.LNorm.Means), main="1000 LogNormal Means")
```

## A Single Proportion

Resampling a single proportion 1000 times is easy.

```{r example}
My.Props <- ResampleProp(rbinom(100, size=1, prob = 0.4))
summary(My.Props)
```

### Plot of the Resampled Proportions

```{r}
plot(density(My.Props), main="1000 Sample Proportions")
```

## Difference of Means

Resampling the difference in two means.


```{r ex3}
My.LNorm.Means2 <- ResampleDiffMeans(rlnorm(100), rlnorm(100, meanlog = 0.7))
summary(My.LNorm.Means2)
```

### Plot of the Resampled Means

```{r}
plot(density(My.LNorm.Means2), main="1000 Difference of Means")
```

## Twp Proportions

Resampling a difference in proportions 1000 times is easy.

```{r ex4}
My.Props2 <- ResampleDiffProps(rbinom(100, size=1, prob = 0.4),rbinom(100, size=1, prob = 0.5))
summary(My.Props2)
```

### Plot of the Resampled Difference in Proportions

```{r}
plot(density(My.Props2), main="1000 Differences in Proportions")
```
